Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-21 paper_jasa.tex
model only plot and experiment3 plot removed

\begin{figure}[hbtp]
   \centering
       \scalebox{0.70}{\includegraphics{power_mixed.pdf}}
       \caption{The overall power estimated from model \ref{mixed} are shown. The corresponding power curve for conventional test is shown for comparison.}
       \label{fig:power_mixed}
\end{figure}

@@

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.4}{\includegraphics{power_loess_exp3.pdf}}
       \caption{Observed power shown by loess smoother with simultaneous bootstrap confidence band and the power of conventional test for sample size $n= 100$ and $\sigma = 5$ as per experiment 3. Notice that for experiment 3, power does not seem to depend on the parameter $\beta$. \blue{Di/Heike, I am not sure how I can relate this to demonstrate the power of visual inference when normal conditions are not met. Does this really test our hypothesis $H_0: \beta=0$ or some other hypothesis about the existence of cluster in the data?}}
       \label{fig:power_loess3}
\end{figure*}

>>>>

%
%\begin{figure}[hbtp]
%   \centering
%       \scalebox{0.70}{\includegraphics{power_mixed.pdf}}
%       \caption{The overall power estimated from model \ref{mixed} are shown. The corresponding power curve for conventional test is shown for comparison.}
%       \label{fig:power_mixed}
%\end{figure}

@@

%\begin{figure*}[hbtp]
%   \centering
%       \scalebox{0.4}{\includegraphics{power_loess_exp3.pdf}}
%       \caption{Observed power shown by loess smoother with simultaneous bootstrap confidence band and the power of conventional test for sample size $n= 100$ and $\sigma = 5$ as per experiment 3. Notice that for experiment 3, power does not seem to depend on the parameter $\beta$. \blue{Di/Heike, I am not sure how I can relate this to demonstrate the power of visual inference when normal conditions are not met. Does this really test our hypothesis $H_0: \beta=0$ or some other hypothesis about the existence of cluster in the data?}}
%       \label{fig:power_loess3}
%\end{figure*}
